### 2021-02-22 README.Rmd
updated documentation with package data info

>>>>

### Package data

Unexported objects `ped1kg` and `ped1kg_unrel` contain pedigree data obtained from 1000 Genomes FTP (http://ftp.1000genomes.ebi.ac.uk/vol1/ftp/release/20130502/integrated_call_samples_v3.20200731.ALL.ped) for all 2504 individuals with sequencing data, and all individuals unrelated to anyone else in the data (momid, dadid, siblings, second_order, and third_order all =0). See [data-raw/generate_sysdata.R](data-raw/generate_sysdata.R) for details.

```{r}
skater:::ped1kg
skater:::ped1kg_unrel
```
